---
title: "2019 Year in Review"
author: "Forrest Diamond"
date: "January 5, 2019"
output: github_document
---

## Prep the workspace

```{r prep, message = FALSE}
library("tidyverse")
```

## Movies Over Time

Let's have a quick look at my movie watching counts.

```{r watch-counts}

diary <- read.csv(file.path(here::here(), "data", "diary.csv"))

diary %>% 
  mutate(year = lubridate::year(Watched.Date),
         date = lubridate::as_date(Watched.Date)) %>% 
  filter(year == 2019) %>%
  count(date) %>%
  arrange(date) %>%
  mutate(running_total = cumsum(n)) %>%
  ggplot() +
  geom_point(aes(x = date, y = running_total)) +
  labs(x = "Date Watched",
       y = "Cumulative Total",
       title = "That's a lot of movies!") +
  theme_minimal() +
  scale_x_date()

```

## Ratings

Let's see if I'm using the whole scale for my ratings.

```{r ratings}

ratings <- read.csv(file.path(here::here(), "data", "ratings.csv"))

ratings %>% 
  mutate(year = lubridate::year(Date)) %>% 
  filter(year == 2019) %>%
  count(Rating) %>%
  mutate(mean = weighted.mean(Rating, w = n)) %>%
  ggplot() +
  geom_bar(aes(x = Rating, y = n, fill = Rating), stat = "identity") + 
  geom_vline(aes(xintercept = mean), color = "red", alpha = 0.5, size = 3) +
  theme_minimal() +
  labs(x = "Rating",
       y = "Number of Films") +
  scale_fill_viridis_c(limits = c(1, 5))

```

I might have the spread down, but it looks like I'm not labelling enough movies in the middle. What if I simplified this by only using five buckets?

```{r simplified-ratings}

ratings <- read.csv(file.path(here::here(), "data", "ratings.csv"))

ratings %>% 
  mutate(year = lubridate::year(Date)) %>% 
  filter(year == 2019) %>%
  count(Rating) %>%
  mutate(is_split = ifelse(Rating - floor(Rating) > 0.1, T, F)) %>%
  left_join({.} %>%
              filter(is_split) %>%
              mutate(Rating = floor(Rating)) %>%
              mutate(floor_n = n / 2) %>%
              select(Rating, floor_n),
            by = "Rating") %>%
  left_join({.} %>%
              filter(is_split) %>%
              mutate(Rating = ceiling(Rating)) %>%
              mutate(ceiling_n = n / 2) %>%
              select(Rating, ceiling_n),
            by = "Rating") %>%
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>%
  mutate(total_n = n + floor_n + ceiling_n) %>%
  filter(!is_split) %>%
  select(Rating, total_n) %>%
  ggplot() +
  geom_bar(aes(x = Rating, y = total_n, fill = Rating), stat = "identity") + 
  theme_minimal() +
  labs(x = "Rating",
       y = "Number of Films") +
  scale_fill_viridis_c(limits = c(1, 5))

```

Yup, not enough threes, too many twos and fours.

## Top Movies

Now let's see the best movies I saw this year, and the best movies from this year.

```{r top-movies}

ratings <- read.csv(file.path(here::here(), "data", "ratings.csv"), fileEncoding = "UTF-8")

ratings %>% 
  mutate(year_watched = lubridate::year(Date)) %>% 
  filter(year_watched == 2019) %>%
  mutate(Rank = rank(-Rating, ties.method = "random")) %>% 
  filter(Rank <= 10) %>% 
  ggplot() +
  geom_bar(aes(x = Rank, y = Rating, fill = Rating), stat = "identity") +
  geom_text(aes(x = Rank, y = 0, label = Name), hjust = 0) +
  theme_minimal() +
  coord_flip() +
  scale_x_reverse() +
  scale_fill_viridis_c(limits = c(1, 5))


```

Wow, not a lot of movies made in 2019 on that list. What if we only look at those?

```{r top-movies-2019}

ratings <- read.csv(file.path(here::here(), "data", "ratings.csv"), fileEncoding = "UTF-8")

ratings %>% 
  filter(Year == 2019) %>%
  mutate(Rank = rank(-Rating, ties.method = "random")) %>% 
  filter(Rank <= 10) %>% 
  ggplot() +
  geom_bar(aes(x = Rank, y = Rating, fill = Rating), stat = "identity") +
  geom_text(aes(x = Rank, y = 0, label = Name), hjust = 0) +
  theme_minimal() +
  coord_flip() +
  scale_x_reverse() +
  scale_fill_viridis_c(limits = c(1, 5))

```

That feels like a decent list, to me.

## Reviews

I don't think I did a great job recording reviews- how'd I do?

```{r reviews}

reviews <- read_csv(file.path(here::here(), "data", "reviews.csv"))

reviews %>% 
  filter(lubridate::year(`Watched Date`) == 2019) %>%
  nrow()

```

Not bad...

## 2020 Goals

- [ ] Watch 150 Movies
- [ ] Write 75 Reviews
- [ ] Get closer to a normal distribution in my ratings